Painting with Triangles

### 2014-04-22 paper.tex
foo

% uncomment one the following two lines, first one showing pictures
%\documentclass[review]{acmsiggraph}
\documentclass[review,draft]{acmsiggraph}

@@

% comment out this line to get figures; uncomment for fast latex
\usepackage[draft]{graphicx}
%\usepackage{graphicx}

@@

\section{Discussion and Results}
Paintings made with our system can be seen in Figures~\ref{fig:teaser}, \ref{fig:face},  \ref{fig:stop} and \ref{fig:boxes}.  Here we first consider how the complexity of the algorithm grows both in time and geometry.
The results from this analysis and our experience with the system have lead to a number of observations.

@@

\begin{figure*}
    \centering
        \includegraphics[width=0.195\textwidth]{images/zoom61}
        \includegraphics[width=0.195\textwidth]{images/zoom62}
        \includegraphics[width=0.195\textwidth]{images/zoom63}
        \includegraphics[width=0.195\textwidth]{images/zoom64}
        \includegraphics[width=0.195\textwidth]{images/zoom65}
        \includegraphics[width=0.195\textwidth]{images/zoom66}
        \includegraphics[width=0.195\textwidth]{images/zoom67}
        \includegraphics[width=0.195\textwidth]{images/zoom68}
        \includegraphics[width=0.195\textwidth]{images/zoom69}
        \includegraphics[width=0.195\textwidth]{images/zoom72}
    \caption{A painting that shows extreme zoom levels.  The final image is at zoom level 524,000:1, for an effective resolution equivalent to an image with more than $10^{17}$ pixels.}
    \label{fig:boxes}
\end{figure*}

>>>>

% uncomment one the following two lines, first one showing pictures
\documentclass[review]{acmsiggraph}
%\documentclass[review,draft]{acmsiggraph}

@@

% comment out this line to get figures; uncomment for fast latex
\usepackage{graphicx}

@@

\section{Results and Discussion}
Paintings made with our system can be seen in Figures~\ref{fig:teaser}, \ref{fig:face},  \ref{fig:stop} and \ref{fig:boxes}.  
%
These figures contain drawings in a range of styles. The images shown in \fig{fig:boxes}
reveal a drawing with an extreme zoom range up to 524,000:1, 
for an effective resolution equivalent to an image with more than $10^{17}$ pixels.
At this zoom level our render begins to reach the limits of floating point precision
for single floats; this could be ameliorated by switching to double-precision.

Next we  consider how the complexity of the algorithm grows both in time and geometry.
The results from this analysis and our experience with the system have lead to a number of observations.

@@

\begin{figure*}
    \centering
        \includegraphics[width=0.195\textwidth]{images/zoom61}
        \includegraphics[width=0.195\textwidth]{images/zoom62}
        \includegraphics[width=0.195\textwidth]{images/zoom63}
        \includegraphics[width=0.195\textwidth]{images/zoom64}
        \includegraphics[width=0.195\textwidth]{images/zoom65}
        \includegraphics[width=0.195\textwidth]{images/zoom66}
        \includegraphics[width=0.195\textwidth]{images/zoom67}
        \includegraphics[width=0.195\textwidth]{images/zoom68}
        \includegraphics[width=0.195\textwidth]{images/zoom69}
        \includegraphics[width=0.195\textwidth]{images/zoom72}
    \caption{A painting that shows extreme zoom levels.  The final image is at zoom level 524,000:1.}
    \label{fig:boxes}
\end{figure*}
